Incentivizing Exploration by Heterogeneous Users

### 2018-02-17 algorithm.tex
cleaned up the technical section

\section{Main Algorithm and Analysis}
\label{sec:ub}

\dkcomment{Here and earlier, we are using a lot of displayed
  equations. We could inline some/many of them to save space.}

The algorithm achieving the claimed bounds of
Theorems~\ref{rst:budget} and~\ref{rst:regret} is fairly simple.
It mostly allows agents to exploit, but when an arm is sufficiently
unlikely to be pulled, 
the algorithm incentivizes this arm with a payment high enough
to guarantee that the next agent pulls it.
This way the algorithm ensures that each arm is pulled often enough.

@@

When multiple arms are payment-eligible, the algorithm picks one
uniformly at random to incentivize.
\dkcomment{Is uniform randomness used anywhere? Does arbitrary work?}
When the algorithm decides to incentivize an arm $i$,
it offers ``whatever it takes,'' i.e., offers a payment of
$\Pay{t}{i} = \max_{\AgV,i'} \AgV \cdot (\ArmEV{t}{i'} - \ArmEV{t}{i})$.
The maximum for \AgV is taken over the support of \AgentDist;
recall that we assumed this support to be compact.
The payment \Pay{t}{i} may appear unnecessarily high.
Indeed, it suffices to
incentivize only a $1/\log(s)$ fraction of the agents,
and our bounds also hold for an alternate version of our algorithm that 
offers payment
$\Pay{t}{i} = \min \Set{c \geq 0}{%
\Prob[\AgV \sim \AgentDist]{c + \AgV \cdot \ArmEV{t}{i} \geq \max_{i'\ne i} \AgV \cdot \ArmEV{t}{i'}} \ge 1/\log(s)}$.
However, we focus on the higher payments for simplicity of presentation.

@@

\begin{algorithm}
\caption{Algorithm: Incentivizing Exploration \label{alg:basic-incentivizing}}
\begin{algorithmic}
\STATE Set the current phase number $s = 1$.
\COMMENT{Each arm is pulled once initially ``for free''.}
\FOR{time steps $t = 1, 2, 3, \ldots$}
\IF{$\NumPull{t}{i} \geq \dkedit{s+1}$ for all arms $i$}
\STATE Increment the phase $s = s + 1$.
\ENDIF
\IF{there is a payment-eligible arm $i$}
\STATE Let $i$ be a uniformly random payment-eligible arm.
\dkcomment{Is uniform randomness used anywhere?}
\STATE Offer payment
$\Pay{t}{i} = \max_{\AgV,i'} \AgV \cdot (\ArmEV{t}{i'} - \ArmEV{t}{i})$
for pulling arm $i$
(and payment 0 for all other arms).
\ELSE
\STATE Let agent $t$ play myopically, i.e., offer payments 0 for all arms.
\ENDIF
\ENDFOR
\end{algorithmic}
\end{algorithm}

@@

To capture the probability masses of problematic agents,
we define the quantity
$\AlmostTied{\delta} = \Prob[\AgV \sim \AgentDist]{%
\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq \delta}$
to be the total probability mass (across all arms) of agents
whose (actual) preference for their best arm over their second-best
arm is at most $\delta$.
\pfcomment{We can check through the whole paper on whether we write
$\AgV \sim \AgentDist$, $\AgentDist$ or $\AgV$ in the subscript, and make the use consistent.
  Here we write $\AgV \sim \AgentDist$ while we have only $\AgentDist$ in the definition of $p$ in the problem description.}
%The minimum probability mass of users who prefer their best arm
%sufficiently strongly over their second-best arm is denoted by
%$\ClearPref{\delta} = \min_{i}
%\Prob[\AgV \sim \AgentDist]{\Best{\AgV}=i,%
%\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) > \delta}$.
%Notice that \AlmostTied{\delta} (being a measure of problematic
%agents) is defined as a sum over all arms,
%while  \ClearPref{\delta} (being a measure of non-problematic agents)
%is defined as a minimum over arms.
%Also notice that $\ClearPref{0} = \MinProb$.
\dkcomment{We should stress somewhere that we assume that actual ties
  have measure 0.}

\dkcomment{We weren't using $p(\delta)$ anywhere, so I got rid
  of it.}

@@

Next, we show the complementary part:
when \AccE{t}{x} happens, no myopic agent incurs large regret.

@@

\begin{proof}
By definition, when \AccEU{t}{x} happens,
for all arms $i$ and attributes $j$,
all arm attribute estimates are accurate to within $x$,
in the sense that
$|\ArmE{\tau}{i}{j} - \Arm{i}{j}| \leq x$.

@@

\dkcomment{I'm leaving in all the dependencies on ``constant''
  parameters for now. We can decide later which ones to absorb into
  big-$O$.}
\end{proof}

>>>>

\section{Main Algorithm and Analysis}
\label{sec:ub}
The algorithm achieving the claimed bounds of
Theorems~\ref{rst:budget} and~\ref{rst:regret} is fairly simple.
It mostly allows agents to exploit, but when an arm is sufficiently
unlikely to be pulled, 
the algorithm incentivizes this arm with a payment high enough
to guarantee that the next agent pulls it.
This way the algorithm ensures that each arm is pulled often enough.

@@

When multiple arms are payment-eligible, the algorithm picks one arbitarily to incentivize.
When the algorithm decides to incentivize an arm $i$,
it offers ``whatever it takes,'' i.e., offers a payment of
$\Pay{t}{i} = \max_{\AgV,i'} \AgV \cdot (\ArmEV{t}{i'} - \ArmEV{t}{i})$.
The maximum for \AgV is taken over the support of \AgentDist;
recall that we assumed this support to be compact.
The payment \Pay{t}{i} may appear unnecessarily high.
Indeed, it suffices to
incentivize only a $1/\log(s)$ fraction of the agents,
and our bounds also hold for an alternate version of our algorithm that 
offers payment
$\Pay{t}{i} = \min \Set{c \geq 0}{%
\Prob[\AgV \sim \AgentDist]{c + \AgV \cdot \ArmEV{t}{i} \geq \max_{i'\ne i} \AgV \cdot \ArmEV{t}{i'}} \ge 1/\log(s)}$.
However, we focus on the higher payments for simplicity of presentation.

@@

\begin{algorithm}
\caption{Algorithm: Incentivizing Exploration \label{alg:basic-incentivizing}}
\begin{algorithmic}
\STATE Set the current phase number $s = 1$.
\COMMENT{Each arm is pulled once initially ``for free''.}
\FOR{time steps $t = 1, 2, 3, \ldots$}
\IF{$\NumPull{t}{i} \geq s+1$ for all arms $i$}
\STATE Increment the phase $s = s + 1$.
\ENDIF
\IF{there is a payment-eligible arm $i$}
\STATE Let $i$ be an arbitary payment-eligible arm.
\STATE Offer payment
$\Pay{t}{i} = \max_{\AgV,i'} \AgV \cdot (\ArmEV{t}{i'} - \ArmEV{t}{i})$
for pulling arm $i$
(and payment 0 for all other arms).
\ELSE
\STATE Let agent $t$ play myopically, i.e., offer payments 0 for all arms.
\ENDIF
\ENDFOR
\end{algorithmic}
\end{algorithm}

@@

To capture the probability masses of problematic agents,
we define the quantity
$\AlmostTied{\delta} = \Prob[\AgV \sim \AgentDist]{%
\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq \delta}$
to be the total probability mass (across all arms) of agents
whose (actual) preference for their best arm over their second-best
arm is at most $\delta$.
\dkcomment{We should stress somewhere that we assume that actual ties
  have measure 0.}

@@

Next, we show the complementary part:
when \AccEU{t}{x} happens, no myopic agent incurs large regret.

@@

\begin{proof}
By definition, when \AccEU{t}{x} happens,
for all arms $i$ and attributes $j$,
all arm attribute estimates are accurate to within $x$,
in the sense that
$|\ArmE{t}{i}{j} - \Arm{i}{j}| \leq x$.

@@

\end{proof}

### 2018-02-17 payment-proof.tex
cleaned up the technical section

\[
  \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x_n^2}{16 \sigma^2}}
\; \leq \;
  5 n^{3/5} + \frac{\sqrt{n} x_n}{4 \sigma}
\; = \; 
  5 n^{3/5} + (\ell-1)
  \; \leq \; \frac{n x'_n}{2 \sigma}.
\]

\dkcomment{Unless I made a calculation mistake, we could replace a 12
  with a 10.}

Applying Lemma~\ref{lem:round-prob} to $\tau_{i,j}$,
we conclude that the probability that the error in coordinate $j$ of
arm $i$ exceeds $x'_s = g(s,\ell-1)$ at time $\tau_{i,j}$
(and hence at any time, by definition of $\tau_{i,j}$)
is at most
$24 \exp\left(-\frac{1.8 s x_s^2}{16 \sigma^2} \right)
\; = \; 24 \exp(-1.8 (\ell-1)^2)$.
Now, taking a union bound over all arms $i$ and
coordinates $j$ completes the proof.
\end{proof}

>>>>

\[
  \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x_n^2}{16 \sigma^2}}
\; \leq \;
  5 n^{3/5} + \frac{\sqrt{n} x_n}{4 \sigma}
\; = \; 
  5 n^{3/5} + (\ell-1)
  \; \leq \; \frac{n x'_n}{2 \sigma}.
\]
Applying Lemma~\ref{lem:round-prob} to $\tau_{i,j}$,
we conclude that the probability that the error in coordinate $j$ of
arm $i$ exceeds $x'_s = g(s,\ell-1)$ at time $\tau_{i,j}$
(and hence at any time, by definition of $\tau_{i,j}$)
is at most
$24 \exp\left(-\frac{1.8 s x_s^2}{16 \sigma^2} \right)
\; = \; 24 \exp(-1.8 (\ell-1)^2)$.
Now, taking a union bound over all arms $i$ and
coordinates $j$ completes the proof.
\end{proof}
